Software Defect Prediction: Review, Commentary, and Future Work

### 2015-12-15 paper/paper.tex
fixed citation

\subsection{Context Factors}
Context factors for projects were assessed by Fend at el (2014 cite here). Used as a measurement of project similarity. The provides a set of measurements to rank a project's relatedness when performing cross-project defect prediction.

>>>>

\subsection{Context Factors}
Context factors for projects were assessed by Feng et al \cite{Zhang:2014:TBU:2597073.2597078}  Used as a measurement of project similarity. The provides a set of measurements to rank a project's relatedness when performing cross-project defect prediction.
